### 2014-11-12 locks.tex
make it a table
Remove unneeded subfloats.

\begin{topfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=6.5cm]{results/locks/sssp-locks.png}}
   \end{center}
  \scap{locks:SSSP}{Locking statistics for SSSP.
     \texttt{Coordinated} refers to the program in
     Fig.~\ref{results:sssp_uspowergrid}, while \texttt{Buffered} is a more
     optimized version of the same program where coordination operations are
     buffered before application.}
\end{topfig}

@@

\begin{topfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=6.5cm]{results/locks/ht-locks.png}}
   \end{center}
  \scap{locks:HT}{Locking statistics for HT. Coordination reduces
     the overall number of locks used, while further optimization for locality
     reduces the locks even further.}
\end{topfig}

@@

\begin{topfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=6.5cm]{results/locks/bp.png}}
   \end{center}
  \scap{locks:LBP}{Locking statistics for LBP and SBP. Locking is constant for
     SBP because threads do not interact with each other.}
\end{topfig}

>>>>

\begin{topfig}
   \begin{center}
      \includegraphics[width=6.5cm]{results/locks/sssp-locks.png}
   \end{center}
  \scap{locks:SSSP}{Locking statistics for SSSP.
     \texttt{Coordinated} refers to the program in
     Fig.~\ref{results:sssp_uspowergrid}, while \texttt{Buffered} is a more
     optimized version of the same program where coordination operations are
     buffered before application.}
\end{topfig}

@@

\begin{topfig}
   \begin{center}
      \includegraphics[width=6.5cm]{results/locks/ht-locks.png}
   \end{center}
  \scap{locks:HT}{Locking statistics for HT. Coordination reduces
     the overall number of locks used, while further optimization for locality
     reduces the locks even further.}
\end{topfig}

@@

\begin{topfig}
   \begin{center}
      \includegraphics[width=6.5cm]{results/locks/bp.png}
   \end{center}
  \scap{locks:LBP}{Locking statistics for LBP and SBP. Locking is constant for
     SBP because threads do not interact with each other.}
\end{topfig}
